---
execute:
  echo: false
  warning: false
title: "September 2026 Primary Candidates"
description: "Democratic and Republican candidates in contested Massachusetts legislative primaries for the September 1, 2026 state primary, by district."
canonical-url: true
---

```{r}
library(here)
source(here("_gen/legislative_info.R"))
```

Candidates on the ballot for the **`r PRIMARY_2026_DATE`** Massachusetts state
primary, for every legislative district with a contested primary — that is,
where more than one candidate of the same party is running. Districts where
both parties field a single candidate are not listed.

Where a district is contested for one party only, the other party's candidate
is shown marked *unopposed*. Sitting legislators are marked *incumbent*, and
seats whose incumbent is not seeking re-election are flagged as open. District
names link to the full district page with maps, demographics, and election
history.

```{r}
primary_2026_summary_table()
```

## State Representative

```{r, results='asis'}
primary_2026_office_section("State Representative")
```

## State Senate

```{r, results='asis'}
primary_2026_office_section("State Senate")
```

## Governor's Council

```{r, results='asis'}
primary_2026_office_section("Governor's Council")
```

## U.S. House

```{r, results='asis'}
primary_2026_office_section("U.S. House")
```
